Efficiency

### 2018-09-14 Second.Rnw
with first picture in
four  pics

>>>>

\begin{figure}[h]
\captionsetup{width=0.7\textwidth}
\includegraphics[width=0.7\textwidth, center]{roteff1.png}
\caption{One text's explanations of the variance between open-water efficiency and behind a hull from page 152 of \parencite{lewis1988}}
\label{fig:roteff1.png}
\end{figure}

\begin{figure}[h]
\captionsetup{width=0.7\textwidth}
\includegraphics[width=0.7\textwidth, center]{roteff2.png}
\caption{One text's explanations of the variance between open-water efficiency and behind a hull from page 131 of \parencite{Carlton2007}}
\label{fig:roteff2.png}
\end{figure}

\begin{figure}[h]
\captionsetup{width=0.7\textwidth}
\includegraphics[width=0.7\textwidth, center]{roteff3.png}
\caption{One text's explanations of the variance between open-water efficiency and behind a hull from page 14 of \parencite{MAN2017}}
\label{fig:roteff3.png}
\end{figure}

\begin{figure}[h]
\captionsetup{width=0.7\textwidth}
\includegraphics[width=0.7\textwidth, center]{roteff4.png}
\caption{One text's explanations of the variance between open-water efficiency and behind a hull from page 411 of \parencite{Mollard2011}}
\label{fig:roteff4.png}
\end{figure}
